%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research \& Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Post-Doctoral Research Fellow} % Job title
    {Stockholm University} % Organization
    {Stockholm, Sweden} % Location
    {March. 2023 - Ongoing} % Date(s)
    {
    Post-doctoral research fellow working with Prof. Jens Jasche and Prof. Hiranya Peiris on bayesian hierarchical models for LSST DESC (50\% FTE in-kind contributions).
    }

%---------------------------------------------------------
  \cventry
    {Senior Scientist/Developer (50\% FTE until Oct. 2022)} % Job title
    {University of Edinburgh} % Organization
    {Edinburgh, United Kingdom} % Location
    {Sept. 2021 - Feb. 2023} % Date(s)
    {
    Euclid SGS Senior Scientist/Developer working with Prof. Andy Taylor on weak lensing shape measurement calibration and sensitivity.
    }

%---------------------------------------------------------
  \cventry
    {Research Fellow (50\% FTE from Sept. 2021)} % Job title
    {University College London} % Organization
    {London, United Kingdom} % Location
    {Apr. 2020 - Sept. 2022} % Date(s)
    {
    UCL Research Fellow working with Prof. Benjamin Joachimi on Bayesian methods for cosmological galaxy surveys such as the Euclid Satellite.
    }
    
 \cventry
    {Post-Doctoral Research Associate (Currently Visiting Researcher)} % Job title
    {Imperial College London} % Organization
    {London, United Kingdom} % Location
    {Dec. 2019 - PRESENT} % Date(s)
    {
    PDRA working with Prof. Alan Heavens and Prof. Andrew Jaffe on Bayesian Hierarchical Models for Cosmic Shear on the sphere.
    %   \begin{cvitems} % Description(s) of tasks/responsibilities
    %     \item {Euclid Consortium PDRA}
    %     \item {Pipeline development, testing, implementation, and validation for Weak Lensing Measurements}
    %     \item {Line manager: Dr. Benjamin Joachimi}
    %   \end{cvitems}
    }

  \cventry
    {Post-Doctoral Research Assistant} % Job title
    {University College London} % Organization
    {London, United Kingdom} % Location
    {Dec. 2018 - Dec. 2019} % Date(s)
    {
    Euclid SGS PDRA working with Prof. Benjamin Joachimi on pipeline development, testing, and validation for Weak Lensing power spectra.
    %   \begin{cvitems} % Description(s) of tasks/responsibilities
    %     \item {Euclid Consortium PDRA}
    %     \item {Pipeline development, testing, implementation, and validation for Weak Lensing Measurements}
    %     \item {Line manager: Dr. Benjamin Joachimi}
    %   \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
