%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Outreach}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%   \cventry
%     {Social Media Engagement: #AstroThreadBR \& #AstroMiniBR} % Role
%     {Engagement with the science enthusiast community via the #AstroThreadBR and #AstroMiniBR projects using twitter threads to educate the public about astronomy related topics.} % Event
%     {YouTube} % Location
%     {2020} % Date(s)
%     {
%       {Outreach talk for Astronomy on Tap London, live on YouTube. URL: https://youtu.be/MLwBvdc675A}
%     }
    
  \cventry
    {Social Media Engagement} % Role
    {Project Collaborator for \#AstroThreadBR and \#AstroMiniBR } % Event
    {Twitter} % Location
    {2019-PRESENT} % Date(s)
    {
      {Engagement with the science enthusiasts community in Brazil via the \#AstroThreadBR and \#AstroMiniBR projects using twitter threads to educate the general public about astronomy. Threads have, on average, a reach of 10-20k impressions.}
    }

  \cventry
    {Public Engagement Talk} % Role
    {Talk: ``Weighing Ghost Particles with the Universe"} % Event
    {YouTube} % Location
    {2020} % Date(s)
    {
      {Outreach talk for Astronomy on Tap London, live on YouTube. URL: https://youtu.be/MLwBvdc675A}
    }

%---------------------------------------------------------
  
  \cventry
    {Press Release} % Role
    {Article: ``Ghost particles: how galaxies helped us weigh the lightest neutrino"} % Event
    {The Conversation} % Location
    {2019} % Date(s)
    {
      {Article published at The Conversation portal related to Loureiro et al. 2019b , informing the general public about the main results in the paper.}
    }

%---------------------------------------------------------

 \cventry
    {Public Engagement Talk} % Role
    {Talk: ``Hunting Ghosts with Galaxies"} % Event
    {Porto Alegre, BR} % Location
    {2018} % Date(s)
    {
      {Outreach talk at a high school about Cosmology, Neutrinos, and data science.}
    }

%---------------------------------------------------------
  \cventry
    {Art Exhibition} % Role
    {If a Tree falls in the Forrest: Cosmology meets Art} % Event
    {Grizdale Forest, UK} % Location
    {2018} % Date(s)
    {
      {Art exhibition in collaboration with the Royal College of Arts. Presentation of a workpiece "Confirmation of Time” in collaboration with the artist Franziska Hatton. URL: http://ifatreefalls.rca.ac.uk}
    }

%---------------------------------------------------------
  \cventry
    {Royal Academy of Arts Lates} % Role
    {L'Observatoire Bizarre } % Event
    {London, UK} % Location
    {2018} % Date(s)
    {
    {Public engagement in collaboration with the Royal College of Arts at the Dada \&
Surrealism RA Late. Organised by Dr. Andrew Pontzen and Michaela French.}
    }

  \cventry
    {Public Engagement Talk} % Role
    {Physics Club: ``Time in Cosmology"} % Event
    {Porto Alegre, BR} % Location
    {2015} % Date(s)
    {
  {Outreach talk at the Physics Club, Universidade Federal do Rio Grande do Sul.}
    }
%---------------------------------------------------------
\end{cventries}
